---
title: 'Topic 3 Effective Visualization'
author: "Amin G. Alhashim"
date: "9/13/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load all required packages

```{r, results='hide'}
library(mdsr)
library(tidyverse)
library(kableExtra)
```

# CIACountries Data

This is an example in [Chapter 3 A gramer for graphics](https://mdsr-book.github.io/mdsr2e/ch-vizII.html) of Modern Data Science with R book.

Filtering out observation with NA values

```{r}
temp <- CIACountries %>% na.omit()
```

Printing the first few observations

```{r}
head(temp) %>% 
  kbl() %>% 
  kable_styling(
    fixed_thead = T, 
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```

Investigating the relationship between `gdp` and `educ` by mapping them to the `x` and `y` (position) visual cues, respectively while using an **accessible** color visual cue to represent the categories of percentage of users.

```{r}
ggplot(data = temp) +
  geom_point(mapping = aes(x = educ, y = gdp, color = net_users)) +
  scale_color_viridis_d()
```
