---
title: Plot Maps with ggplot2 Demo
auther: Amin G. Alhashim
---

```{r}
library(ggplot2)
library(dplyr)
library(forcats)
library(tidylog)
```

# Introduction
This file demonstrate 

1. how to access boundary data provided by the `maps` package via the `map_data` function from the `ggplot2` package.
2. how to plot the bounday data usign the `geom_polygon` from the `ggplot2` package

# World

## Border Data

```{r, results='hide'}
map_data("world")
```

Regions, countries here in this case
```{r}
map_data("world") %>% 
  distinct(region)
```

Top regions, countries, with least number of points for their border, least complex borders
```{r}
map_data("world") %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>% 
  head(20) %>% 
  mutate(region = fct_reorder(region, desc(n))) %>% 
  ggplot() +
  geom_col(mapping = aes(y = factor(region), x = n))
```

Top regions, countries, with most number of points for their borders, most complex borders
```{r}
map_data("world") %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(20) %>% 
  mutate(region = fct_reorder(region, desc(n))) %>% 
  # sample_n(20) %>% 
  ggplot() +
  geom_col(mapping = aes(y = factor(region), x = n))
```


## Plot
```{r}
map_data("world") %>% 
  left_join(tribble(~region, ~num,
                    "Australia", 15,
                    "Russia", 20,
                    "France", 15)) %>% 
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```


# USA States

## Border Data
```{r}
map_data("state")
```


Regions, states in this case
```{r}
map_data("state") %>% 
  distinct(region)
```

## Plot
```{r}
map_data("state") %>% 
  left_join(tribble(~region, ~num,
                    "arizona", 10,
                    "minnesota", 20,
                    "wisconsin", 15)) %>% 
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```

# Italy

## Border Data
```{r}
map_data("italy")
```


Regions, administrative units (maybe) in this case
```{r}
map_data("italy") %>% 
  distinct(region)
```

## Plot
```{r}
map_data("italy") %>% 
  left_join(tribble(~region, ~num,
                    "Bolzano-Bozen", 10,
                    "Varese", 20,
                    "Rieti", 15)) %>%
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```


