```{r}
library(ggplot2)
library(dplyr)
library(forcats)
library(tidylog)
```

# World

Data describe the boundary of countries in the world
```{r}
map_data("world")
```

Regions; represent countries in this case
```{r}
map_data("world") %>% 
  distinct(region)
```

Top regions (countries) with least number of points for their description
```{r}
map_data("world") %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>% 
  head(20) %>% 
  mutate(region = fct_reorder(region, n)) %>% 
  ggplot() +
  geom_col(mapping = aes(y = factor(region), x = n))
```

Top regions (countries) with most number of points for their description
```{r}
map_data("world") %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(20) %>% 
  mutate(region = fct_reorder(region, n)) %>% 
  # sample_n(20) %>% 
  ggplot() +
  geom_col(mapping = aes(y = factor(region), x = n))
```


# Plot
```{r}
map_data("world") %>% 
  left_join(tribble(~region, ~num,
                    "Australia", 15,
                    "Russia", 20,
                    "France", 15)) %>% 
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```


# USA

Data
```{r}
map_data("state")
```


Regions; represent states in this case
```{r}
map_data("state") %>% 
  distinct(region)
```

Plot
```{r}
map_data("state") %>% 
  left_join(tribble(~region, ~num,
                    "arizona", 10,
                    "minnesota", 20,
                    "wisconsin", 15)) %>% 
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```

# Italy

Data
```{r}
map_data("italy")
```


Regions; represent administrative units (maybe) in this case
```{r}
map_data("italy") %>% 
  distinct(region)
```

Plot
```{r}
map_data("italy") %>% 
  left_join(tribble(~region, ~num,
                    "Bolzano-Bozen", 10,
                    "Varese", 20,
                    "Rieti", 15)) %>%
  ggplot() + 
  geom_polygon(mapping = aes(x = long, y = lat, group = group, fill = num), 
               color = "white")
```


