```{r 05_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(tidyverse)
library(ggplot2)
library(gplots)
```


# Adding More Aesthetic Attributes {-}

### Exploring SAT Scores {-}

```{r}
education <- read.csv("https://bcheggeseth.github.io/112_spring_2023/data/sat.csv")
```

The first question we'd like to answer is to what degree do per pupil spending (`expend`) and teacher `salary` *explain* this variability? We can start by plotting each against `sat`, along with a best fit linear regression model:


```{r, fig.width=3,fig.height=3,fig.fullwidth=TRUE,fig.show='hold', fig.alt = c('Scatter plot of average SAT scores  against teacher salary across U.S. states in mid-1990s. There is a weak negative relationship.','Scatter plot of average SAT scores  against education expenditure across U.S. states in mid-1990s. There is a weak negative relationship.')}
ggplot(education, aes(y = sat, x = salary)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm") + 
  theme_classic() +
  smplot2::sm_statCorr()

ggplot(education, aes(y = sat, x = expend)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm") + 
  theme_classic() +
  smplot2::sm_statCorr()
```

```{example}
Is there anything that surprises you in the above plots? What are the relationship trends?
```

> ANSWER: 

```{example}
Make a single scatterplot visualization that demonstrates the relationship between `sat`, `salary`, and `expend`. Summarize the trivariate relationship between `sat`, `salary`, and `expend`. 
```

*Hints: 1. Try using the color or size aesthetics to incorporate the expenditure data. 2. Include some model smooths with `geom_smooth()` to help highlight the trends.*

> ANSWER: 

```{r fig.alt = 'Write alt text here'}
#fill in 
ggplot(data = education, aes(x = salary, y = sat, color = cut(expend, 3)))+
  geom_point() +
  geom_smooth(se = FALSE, method = "lm") +
  theme_classic()

```



```{example}
The `fracCat` variable in the `education` data categorizes the fraction of the state's students that take the SAT into `low` (below 15%), `medium` (15-45%), and `high` (at least 45%).
```

a. Make a univariate visualization of the `fracCat` variable to better understand how many states fall into each category.   

> ANSWER: 

```{r fig.alt = 'Write alt text here'}
ggplot(data = education, mapping = aes(x = fracCat)) +
  geom_bar() +
  theme_classic()


```

b. Make a bivariate visualization that demonstrates the relationship between `fracCat` and `sat`. What story does your graphic tell?

> ANSWER: 

```{r fig.alt = 'Write alt text here'}
ggplot(data = education, mapping = aes(y = sat, x = fracCat)) +
  geom_boxplot()

```

c. Make a trivariate visualization that demonstrates the relationship between `fracCat`, `sat`, and `expend`. Incorporate `fracCat` as the color of each point, and use a single call to `geom_smooth` to add three trendlines (one for each `fracCat`). What story does your graphic tell?   

> ANSWER: 

```{r fig.alt = 'Write alt text here'}
ggplot(data = education, mapping = aes(x = expend, y = sat, color = fracCat)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)


```

d. Putting all of this together, explain this example of **Simpson’s Paradox**. That is, why does it appear that SAT scores decrease as spending increases even though the opposite is true?   

> ANSWER: 



## Other Multivariate Visualization Techniques {-}

### Heat maps {-}    

Note that each variable (column) is scaled to indicate states (rows) with high values (yellow) to low values (purple/blue).  With this in mind you can scan across rows & across columns to visually assess which states & variables are related, respectively. You can also play with the color scheme. Type `?cm.colors` in the console to see various options.    

```{r, fig.width=10, fig.height=20, cache=TRUE}
ed <- as.data.frame(education) # convert from tibble to data frame

# convert to a matrix with State names as the row names
row.names(ed) <- ed$State  #added state names as the row names rather than a variable
ed <- ed %>% select(2:8) #select the 2nd through 8th columns
ed_mat <- data.matrix(ed) #convert to a matrix format

heatmap.2(ed_mat,
  Rowv = NA, Colv = NA, scale = "column",
  keysize = .7, density.info = "none",
  col = hcl.colors(256), margins = c(10, 20),
  colsep = c(1:7), rowsep = (1:50), sepwidth = c(0.05, 0.05),
  sepcolor = "white", cexRow = 2, cexCol = 2, trace = "none",
  dendrogram = "none"
)
```     

```{exercise}
What do you notice? What insight do you gain about the variation across U.S. states?
```

> ANSWER: 

**Heat map with row clusters** 

It can be tough to identify interesting patterns by visually comparing across rows and columns.  Including *dendrograms* helps to identify interesting clusters.

```{r, fig.width=10, fig.height=20,cache=TRUE}
heatmap.2(ed_mat,
  Rowv = TRUE, #this argument changed
  Colv = NA, scale = "column", keysize = .7,
  density.info = "none", col = hcl.colors(256),
  margins = c(10, 20),
  colsep = c(1:7), rowsep = (1:50), sepwidth = c(0.05, 0.05),
  sepcolor = "white", cexRow = 2, cexCol = 2, trace = "none",
  dendrogram = "row" #this argument changed
)
```  

```{exercise}
What new insight do you gain about the variation across U.S. states, now that states are grouped and ordered by similarity?
```

> ANSWER: 

**Heat map with column clusters** 

We can also construct a heat map which identifies interesting clusters of columns (variables).

```{r, fig.width=10, fig.height=20, cache=TRUE}
heatmap.2(ed_mat,
  Colv = TRUE, #this argument changed
  Rowv = NA, scale = "column", keysize = .7,
  density.info = "none", col = hcl.colors(256),
  margins = c(10, 20),
  colsep = c(1:7), rowsep = (1:50), sepwidth = c(0.05, 0.05),
  sepcolor = "white", cexRow = 2, cexCol = 2, trace = "none",
  dendrogram = "column" #this argument changed
)
```   

```{exercise}
What new insight do you gain about the variation across U.S. states, now that variables are grouped and ordered by similarity?
```

> ANSWER: 

### Star plots  {-}  

There's more than one way to visualize multivariate patterns. Like heat maps, these star plot visualizations indicate the relative scale of each variable for each state.  With this in mind, you can use the star maps to identify which state is the most "unusual." You can also do a quick scan of the second image to try to cluster states. How does that clustering compare to the one generated in the heat map with row clusters above?    

```{r, fig.width=15, fig.height=18, cache=TRUE, fig.alt = 'Star plot of SAT data geographically arranged. Education policy / finances and SAT scores differs by geographical region in the U.S.'}
stars(ed_mat,
  flip.labels = FALSE,
  locations = data.matrix(as.data.frame(state.center)), #added external data to arrange by geo location
  key.loc = c(-70, 30), cex = 1
)
stars(ed_mat,
  flip.labels = FALSE,
  locations = data.matrix(as.data.frame(state.center)), #added external data to arrange by geo location
  key.loc = c(-70, 30), cex = 1, 
  draw.segments = TRUE #changed argument
)
```  

```{exercise}
What new insight do you gain about the variation across U.S. states with the star plots (arranged geographically) as compared to heat plots?
```
    
> ANSWER:    
