---
title: "Topic 2 Introduction to Data Visualization"
author: "Amin G. Alhashim"
date: "9/11/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load all required packages
```{r, results='hide'}
library(mdsr)
library(tidyverse)
library(kableExtra)
```


# CIACountries Data

This is an example in [Chapter 3 A gramer for graphics](https://mdsr-book.github.io/mdsr2e/ch-vizII.html) of Modern Data Science with R book.

Filtering out observation with NA values
```{r}
temp <- CIACountries %>% na.omit()
```


Printing the first few observations
```{r}
head(temp) %>% 
  kbl() %>% 
  kable_styling(
    fixed_thead = T, 
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```


Investigating the relationship between `gdp` and `educ` by mapping them to the `x` and `y` (position) visual cues, respectively.
```{r}
ggplot(data = temp) +
  geom_point(mapping = aes(x = educ, y = gdp))

# aesthetic can also be introduced in the ggplot
# ggplot(data = temp, mapping = aes(x = educ, y = gdp)) +
#   geom_point()
```

... mapping the `net_users` (categorical) variable to the `color` visual cue.
```{r}
ggplot(data = temp, mapping = aes(x = educ, y = gdp, color = net_users)) +
  geom_point()
```

... faceting the `net_users` to multiple columns
```{r}
ggplot(data = temp, mapping = aes(x = educ, y = gdp, color = net_users)) +
  geom_point() +
  facet_grid(. ~ net_users)
```

... adding histogram layers beneath the facets
```{r}
ggplot(data = temp) +
  geom_histogram(mapping = aes(y = gdp)) +
  geom_point(mapping = aes(x = educ, y = gdp, color = net_users)) +
  facet_grid(. ~ net_users)
```

... going crazy with testing
```{r}
ggplot(data = temp, mapping = aes(x = educ, 
                                  y = gdp, 
                                  color = area, 
                                  size = pop, 
                                  label = country, 
                                  linewidth=pop)) + 
  geom_point() +
  geom_col() +
  geom_text() +
  labs(x = "Spending on Education", 
       y = "GDP", 
       color = "Area", 
       size = "Population", 
       linewidth = "Population")
```

