Load required packages
```{r}
library(gsheet)
library(tidyverse)
```

Read responses from GSheet suing the [gsheet package](https://github.com/maxconway/gsheet)
```{r}
responses <- gsheet2tbl("docs.google.com/spreadsheets/d/1NvSSzcjYY-0TTdL9Nw7jb6zgoIZIFt4dPK1HpYkesLs")

# rename the response column
responses <- responses %>% 
  rename(`fras_level` = `Indicate you current level of frustration with this class`)

responses
```

Plot responses
```{r, fig.height=2, fig.width=3}
responses %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```

Change to factor, order level alphabetically
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = factor(fras_level)) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```

Change to factor, order levels manually
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = fct_relevel(fras_level, c("Very much", "Little bit", "Not at all"))) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```


Change to factor, order levels based on their frequencies (highest to lowest)
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = fct_infreq(fras_level)) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```

Change to factor (if not) then reverses current order of levels
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = fct_rev(fras_level)) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```



Change to factor (if not), rename levels
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = fct_recode(fras_level, "NAA" = "Not at all")) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```


Combine multiple functions
Change to factor, order based on frequency from lowest to highest
```{r, fig.height=2, fig.width=3}
responses %>% 
  mutate(fras_level = fct_rev(fct_infreq(fras_level))) %>% 
  ggplot(aes(x = fras_level)) +
  geom_bar()
```