---
title: "Comp/Stat 112: Tidy Tuesday 9"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

Load required packages
```{r}
library(tidyverse)
```


# Data Context

## Doctor Who Episodes

Doctor Who is an extremely long-running British television program.
The show was revived in 2005, and has proven very popular since then.
To celebrate this year's 60th anniversary of Doctor Who, we have three datasets.

The data this week comes from Wikipedia's [List of Doctor Who episodes](https://en.wikipedia.org/wiki/List_of_Doctor_Who_episodes_(2005%E2%80%93present) via the [{datardis} package](https://cran.r-project.org/package=datardis) by [Jonathan Kitt](https://github.com/KittJonathan/datardis).
Thank you to Jonathan for compiling and sharing this data!

As of 2023-11-24, the data only includes episodes from the "revived" era.
For an added challenge, consider submitting a pull request to the {datardis} package to update the [data-extraction scripts](https://github.com/KittJonathan/datardis/tree/main/misc) to also fetch the "classic" era data!

## Load Data

```{r data_setup}
drwho_episodes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-28/drwho_episodes.csv')
glimpse(drwho_episodes)
```

```{r}
drwho_directors <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-28/drwho_directors.csv')
glimpse(drwho_directors)
```

```{r}
drwho_writers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-28/drwho_writers.csv')
glimpse(drwho_writers)
```


# Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

# Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
