---
title: "Comp/Stat 112: Tidy Tuesday 3"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

```{r data_setup}
# Get the Data
library(tidyverse)

richmondway <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-09-26/richmondway.csv')


```

## Data Context

### Roy Kent F**k count

For Deepsha Menghani's talk on [Data Viz animation and interactivity in Quarto](https://deepshamenghani.github.io/posit_plotly_crosstalk/#/title-slide), she watched each episode of Ted Lasso at 2X speed and diligently noted down every F*bomb and gesture reference, and then made it into the [richmondway R package](https://github.com/deepshamenghani/richmondway)!

What is Ted Lasso and who is Roy Kent? 

[Ted Lasso](https://en.wikipedia.org/wiki/Ted_Lasso) is a TV show that "follows Ted Lasso, an American college football coach who is hired to coach an English soccer team with the secret intention that his inexperience will lead it to failure, but whose folksy, optimistic leadership proves unexpectedly successful."

[Roy Kent](https://ted-lasso.fandom.com/wiki/Roy_Kent) is one of the main characters who goes from captain of AFC Richmond to one of the coaches. Particularly in early seasons, he's a man of few words, but many of them are f**k, expressed in various moods - mad, sad, happy, amused, loving, surprised, thoughtful, and joyous. 

This dataset includes the number, percentage, and context of f**k used in the show for each episode.



More details including the codebook is available [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-09-26)

```{r}
head(richmondway)
```


## Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

> 

```{r}

```

## Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
