---
title: "Comp/Stat 112: Tidy Tuesday 3"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

```{r data_setup}
# Get the Data
library(tidyverse)

grants <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-03/grants.csv')
grant_opportunity_details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-03/grant_opportunity_details.csv')
```

## Data Context

### US Government Grant Opportunities

The R4DS Online Learning Community is a community of learners at all skill levels working together to improve our data-science-related skills. They offer free data-related education through [book clubs](https://r4ds.io/youtube) and free live question-answering on our [Slack](https://r4ds.io/join), and by curating a dataset every week here at TidyTuesday.

R4DS are now a fiscally sponsored project of Open Collective Foundation (<https://opencollective.foundation>), a 501(c)(3) public charity. That means [donations to the R4DS Online Learning Community](https://r4ds.io/donate) are now tax-deductible in the US! It also means that R4DS are now eligible for a number of grants, including some of the grants listed on [Grants.gov](https://www.grants.gov/web/grants/search-grants.html).

R4DS have exported all grants past and present from that site and are making them available here for you to explore and visualize. They also scraped details for all posted grants.

More details including the codebook is available [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-10-03)

```{r}
glimpse(grants)
glimpse(grant_opportunity_details)
```

## Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

## Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
