---
title: "Comp/Stat 112: Tidy Tuesday 5"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

```{r data_setup}
# Get the Data
library(tidyverse)

haunted_places <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-10/haunted_places.csv')
```

## Data Context

### Haunted Places in the United States

Halloween is coming soon, so we're exploring a spooky dataset: a compilation of Haunted Places in the United States. 
The dataset was [compiled by Tim Renner](https://github.com/timothyrenner/shadowlands-haunted-places), using [The Shadowlands Haunted Places Index](https://www.theshadowlands.net/places/), and [shared on data.world](https://data.world/timothyrenner/haunted-places).

We're also using this dataset as a reminder that [several R packages for spatial data are heading to the graveyard next week](https://geocompx.org/post/2023/rgdal-retirement/index.html).
Don't be tricked by their demise!

```{r}
glimpse(haunted_places)
```

## Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

## Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
