---
title: "Comp/Stat 112: Tidy Tuesday 7"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

Load required packages
```{r}
library(tidyverse)
```


# Data Context

## Horror Legends

Happy Halloween! 
To celebrate, this week we're exploring horror legends from [Snopes.com](https://www.snopes.com/)!

> Since urban legends are often a means of expressing our fears about the dangers that ripple just beneath the surface of our seemingly calm and untroubled world, it should come as no surprise that horror legends are one of urban folklore's richest veins. We worry about the terrible accidents we're powerless to prevent, and we fear anonymous killers who choose victims at random. We cannot protect ourselves from the venomous animals who slither undetected into the places where we work, play, and shop, nor can we stop the onslaught of insects who invade our homes and our bodies. We're repulsed by the contaminants that may lurk in our food. We're afraid of foreigners and foreign places. We fear for our childrens' safety in a world full of drugs, kidnappers, and poisons. We never know what gruesome discovery may be waiting around the next corner. And even if we somehow escape all of these horrors, our own vanities may do us in.

You might want to dig into the details of the articles this week -- particularly if the rating is "mixture".
Each observation includes the URL to that article, which you can open directly from R with the `utils::browseURL()` function.

## Load Data

```{r data_setup}
horror_articles <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-10-31/horror_articles.csv')
glimpse(horror_articles)
```

## Explore Data
```{r}
horror_articles %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  summary()
```
## Explore Some Articles

```{r}
utils::browseURL(horror_articles$url[floor(runif(1, min = 1, max = nrow(horror_articles)+1))])
```




# Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

# Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
