---
title: "Comp/Stat 112: Tidy Tuesday 8"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

Load required packages
```{r}
library(tidyverse)
```


# Data Context

## US House Election Results

It's election day in the United States! To celebrate, the data this week comes from the [MIT Election Data and Science Lab](https://electionlab.mit.edu/) (MEDSL). Hat tip this week to the [RStudio GitHub Copilot integration](https://docs.posit.co/ide/user/ide/guide/tools/copilot.html), which suggested the MEDSL.

From the MEDSL's report [New Report: How We Voted in 2022](https://electionlab.mit.edu/articles/new-report-how-we-voted-2022):

> The Survey of the Performance of American Elections (SPAE) provides information about how Americans experienced voting in the most recent federal election. The survey has been conducted after federal elections since 2008, and is the only public opinion project in the country that is dedicated explicitly to understanding how voters themselves experience the election process.

We're specifically providing data on House elections from 1976-2022. Check out the [MEDSL website](https://electionlab.mit.edu/) for additional datasets and tools.

Be sure to cite the MEDSL in your work:

```
@data{DVN/IG0UN2_2017,
author = {MIT Election Data and Science Lab},
publisher = {Harvard Dataverse},
title = {{U.S. House 1976–2022}},
UNF = {UNF:6:A6RSZvlhh8eRZ4+mvT/HRQ==},
year = {2017},
version = {V12},
doi = {10.7910/DVN/IG0UN2},
url = {https://doi.org/10.7910/DVN/IG0UN2}
}
```

## Load Data

```{r data_setup}
house <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-07/house.csv')
glimpse(house)
```


# Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

# Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
