---
title: "Comp/Stat 112: Tidy Tuesday 9"
author: "INSERT STUDENT NAME HERE (COLLABORATOR NAMES HERE)"
output:
  bookdown::html_document2:
    split_by: none
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: true
    number_sections: false
---

Load required packages
```{r}
library(tidyverse)
```


# Data Context

## Diwali Sales Data

This week is Diwali, the festival of lights! The data this week comes from [sales data](https://www.kaggle.com/datasets/saadharoon27/diwali-sales-dataset) for a retail store during the Diwali festival period in India. The data is shared on Kaggle by Saad Haroon.

This week we're sharing Python data analysis examples! There's a few out there, but these ones from [Brushan Shelke](https://www.kaggle.com/code/bhushanshelke69/diwali-data-exploration) or [Vikas Vachheta](https://github.com/vikasvachheta08/Diwali_Sales_Analysis_Using_Python) (see the Diwali_Sales_Analysis.ipynb file for the code) are some data exploration analyses.

## Load Data

```{r data_setup}
house <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-11-14/diwali_sales_data.csv')
glimpse(house)
```


# Research Question

Develop a research question that you are interested in. *You may need to play with the data a little bit to learn more about what the values mean before you decide on a question.*

# Data Visualization

Create a visualization that answers or addresses your research question.

```{r}

```
