The work in this file was inspired by [this YouTube video](https://www.youtube.com/embed/nlcZcWJiyX8/) by Sérgio Costa.

Load packages
```{r}
library(ggplot2)
library(sf)
library(dplyr)
library(tidylog)
```

Read MN counties data downloaded from [Minnesota Legislature](https://www.gis.lcc.mn.gov/html/download.html): Administrative Boundaries section -> Counties, Year 2010 -> Download -> Shapefile. The page was found via a Google search using the term `shape file for minnesota`.  The search could have been done using the term `geojson minnesota` instead.
```{r}
mn <- read_sf("./county2010/", "county2010")
glimpse(mn)
```

Plot using base R--base R creates a plot for each variable in the dataset other than the geometry variable used to define the boundries of the counties
```{r}
plot(mn, max.plot = 26)
```


Plot using ggplot
```{r}
ggplot() +
  geom_sf(data = mn, aes(fill = POPULATION), color='transparent') +
  geom_sf(data = mn, fill='transparent', color = 'white') +
  scale_fill_viridis_b() +
  theme_void()
```

